### 2006-03-24 Documentation/part1.tex
Minor changes to user-defined systematics part

To specify a user-defined $\chi^2$ algorithm, the following function can be used:
\begin{function}
\GLBNS{SetUserChi}
{\tt void glbSetUserChi(int exp,int rule,double (*chi\_func)(double x[]),int dim,%
double centers[],double errors[],char *info)} tells \GLOBES\ to use {\tt chi\_func}
to calculate $\chi^2$ for experiment {\tt exp} and rule {\tt rule} (these parameters
can take the value \GLBC{GLB\_ALL} to specify all experiments or all rules). {\tt dim} is
the number of variables parametrizing the systematical errors, while {\tt centers[]}
and {\tt errors[]} give their central values and standard deviations, respectively.
When \GLOBES\ calls {\tt chi\_func}, the parameter array {\tt x[]} will contain
the values of the systematics parameters for which $\chi^2$ should be calculated.
Deviating from the standard conventions, the entries of {\tt x[]} will start at
index 1.
\end{function}

@@

\begin{quote}{\tt \footnotesize
  double chi2nearfar(double *x)                                                 \\
  \{                                                                            \\
\hspace*{0.5 cm}      double chi2 = 0;                                          \\
\hspace*{0.5 cm}      double chirate, measured\_rate;                           \\
\hspace*{0.5 cm}                                                                \\
\hspace*{0.5 cm}      glbShiftSignalEnergyScale(0, 0, x[5]);   /* Apply E calib. error */ \\
\hspace*{0.5 cm}      glbShiftSignalEnergyScale(1, 0, x[6]);                    \\
\hspace*{0.5 cm}      glbShiftBackgroundEnergyScale(0, 0, x[5]);                \\
\hspace*{0.5 cm}      glbShiftBackgroundEnergyScale(1, 0, x[6]);                \\
\hspace*{0.5 cm}      for (int i=0; i < NBINS; i++) \{                          \\
\hspace*{1.0 cm}        /* Statistical part of chi\textasciicircum2 for far detector */ \\
\hspace*{1.0 cm}        chirate = (x[1]+x[2]) * glbGetSignalBinInRule(0,0,i) +  \\
\hspace*{2.0 cm}                        (x[4]+x[3]) * glbGetBackgroundBinInRule(0,0,i);\\
\hspace*{1.0 cm}        measured\_rate = glbGetObservedBinInRule(0,0,i);        \\
\hspace*{1.0 cm}        chi2 += 2 * (measured\_rate - chirate);                 \\
\hspace*{1.0 cm}        if (measured\_rate > 0  \&\&  chirate > 0)              \\
\hspace*{1.5 cm}          chi2 += 2 * chirate * log(chirate / measured\_rate);  \\
\hspace*{1.0 cm}                                                                \\
\hspace*{1.0 cm}        /* Statistical part of chi\textasciicircum2 for near detector */ \\
\hspace*{1.0 cm}        chirate = (x[1]+x[3]) * glbGetSignalBinInRule(1,0,i) +  \\
\hspace*{2.0 cm}                        (x[4]+x[3]) * glbGetBackgroundBinInRule(1,0,i);\\
\hspace*{1.0 cm}        measured\_rate = glbGetObservedBinInRule(1,0,i);        \\
\hspace*{1.0 cm}        chi2 += 2 * (measured\_rate - chirate);                 \\
\hspace*{1.0 cm}        if (measured\_rate > 0  \&\&  chirate > 0)              \\
\hspace*{1.5 cm}          chi2 += 2 * chirate * log(chirate / measured\_rate);  \\
\hspace*{0.5 cm}      \}                                                        \\
\hspace*{0.5 cm}                                                                \\
\hspace*{0.5 cm}      for (int j=0; j < 6; j++)  /* Penalties */                \\
\hspace*{1.0 cm}        chi2 += square((x[j+1] - sys\_centers[j]) / sys\_errors[j]);\\
\hspace*{0.5 cm}                                                                \\
\hspace*{0.5 cm}      /* The function is called for each exp ->
                                       Assign chi\textasciicircum2/2 to each */ \\
\hspace*{0.5 cm}      return chi2 / 2;                                          \\
  \}                                                                            
}
\end{quote}
}

>>>>

To specify a user-defined $\chi^2$ algorithm, the following function can be used:
\begin{function}
\GLBNS{SetUserChi}
{\tt void glbSetUserChi(int exp,int rule,double (*chi\_func)(double x[]),int dim,%
double centers[],double errors[],char *info)} tells \GLOBES\ to use {\tt chi\_func}
instead of the builtin functions to calculate $\chi^2$ for experiment {\tt exp} and
rule {\tt rule}. These parameters can take the value \GLBC{GLB\_ALL} to specify that
{\tt chi\_func} should be called once for each experiment or each rule. {\tt dim} is
the number of variables parametrizing the systematical errors, while {\tt centers[]}
and {\tt errors[]} give their central values and standard deviations, respectively.
When \GLOBES\ calls {\tt chi\_func}, the parameter array {\tt x[]} will contain
the values of the systematics parameters for which $\chi^2$ should be calculated.
Deviating from the standard conventions, the entries of {\tt x[]} will start at index 1
(The indices for {\tt params} are {\tt errors} in the call to {\tt glbSetUserChi} start
at 0 as usual).
\end{function}

@@

\begin{quote}{\tt \footnotesize
  double chi2nearfar(double *x)                                                 \\
  \{                                                                            \\
\hspace*{0.5 cm}      double chi2 = 0;                                          \\
\hspace*{0.5 cm}      double chirate, measured\_rate;                           \\
\hspace*{0.5 cm}                                                                \\
\hspace*{0.5 cm}      /* Assign complete chi\textasciicircum2 to first experiment */ \\
\hspace*{0.5 cm}      if (glbGetCurrentExp() != 0)  return 0;                   \\
\hspace*{0.5 cm}                                                                \\
\hspace*{0.5 cm}      glbShiftSignalEnergyScale(0, 0, x[5]);   /* Apply E calib. error */ \\
\hspace*{0.5 cm}      glbShiftSignalEnergyScale(1, 0, x[6]);                    \\
\hspace*{0.5 cm}      glbShiftBackgroundEnergyScale(0, 0, x[5]);                \\
\hspace*{0.5 cm}      glbShiftBackgroundEnergyScale(1, 0, x[6]);                \\
\hspace*{0.5 cm}      for (int i=0; i < NBINS; i++) \{                          \\
\hspace*{1.0 cm}        /* Statistical part of chi\textasciicircum2 for far detector */ \\
\hspace*{1.0 cm}        chirate = (x[1]+x[2]) * glbGetSignalBinInRule(0,0,i) +  \\
\hspace*{2.0 cm}                        (x[4]+x[3]) * glbGetBackgroundBinInRule(0,0,i);\\
\hspace*{1.0 cm}        measured\_rate = glbGetObservedBinInRule(0,0,i);        \\
\hspace*{1.0 cm}        chi2 += 2 * (measured\_rate - chirate);                 \\
\hspace*{1.0 cm}        if (measured\_rate > 0  \&\&  chirate > 0)              \\
\hspace*{1.5 cm}          chi2 += 2 * chirate * log(chirate / measured\_rate);  \\
\hspace*{1.0 cm}                                                                \\
\hspace*{1.0 cm}        /* Statistical part of chi\textasciicircum2 for near detector */ \\
\hspace*{1.0 cm}        chirate = (x[1]+x[3]) * glbGetSignalBinInRule(1,0,i) +  \\
\hspace*{2.0 cm}                        (x[4]+x[3]) * glbGetBackgroundBinInRule(1,0,i);\\
\hspace*{1.0 cm}        measured\_rate = glbGetObservedBinInRule(1,0,i);        \\
\hspace*{1.0 cm}        chi2 += 2 * (measured\_rate - chirate);                 \\
\hspace*{1.0 cm}        if (measured\_rate > 0  \&\&  chirate > 0)              \\
\hspace*{1.5 cm}          chi2 += 2 * chirate * log(chirate / measured\_rate);  \\
\hspace*{0.5 cm}      \}                                                        \\
\hspace*{0.5 cm}      for (int j=0; j < 6; j++)  /* Penalties */                \\
\hspace*{1.0 cm}        chi2 += square((x[j+1] - sys\_centers[j]) / sys\_errors[j]);\\
\hspace*{0.5 cm}      return chi2;                                              \\
  \}                                                                            
}
\end{quote}
}
